\begin{thebibliography}{00}

\bibitem{blumensath}
\textsc{Blumensath} A., \emph{An algebraic proof of Rabin's theorem}, Theoretical Computer Science \textsc{478}, pp. 1--21, 2013.

\bibitem{bp}
\textsc{Boja\'nczyk} M., \textsc{Place} T., \emph{Regular Languages of Infinite Trees That Are Boolean Combinations of Open Sets}, ICALP (2) \textsc{2012}, 104--115.

\bibitem{bojtrees}
\textsc{Boja\'nczyk} M., \emph{Algebra for trees}, In Handbook of Automata Theory, European
Mathematical Society Publishing House, to appear.

\bibitem{bojidziaszek}
\textsc{Boja\'nczyk} M., \textsc{Idziaszek} I., \emph{Algebra for infinite forests with an
application to the temporal logic EF}, CONCUR \textsc{2009}, 131--145.


\bibitem{cklvb}
\textsc{Colcombet} T., \textsc{Kuperberg} D., \textsc{Löding} C., and \textsc{Vanden Boom} M., \emph{Deciding the weak definability of Büchi definable tree languages}, CSL \textsc{2013}, 215--230.

%\bibitem{dup95}
%\textsc{Duparc} J., \emph{The Normal Form of Borel Sets of Finite Rank}, PhD Thesis (in French), University of Paris 7, \textsc{1995}.

\bibitem{dup1}
\textsc{Duparc} J., \emph{Wadge Hierarchy and Veblen Hierarchy Part 1: Borel Sets of Finite Rank}, Journal of Symbolic Logic \textsc{66} (1), 56--86, 2001.

%\bibitem{dupinf}
%\textsc{Duparc} J. : Wadge Hierarchy and Veblen Hierarchy Part 2: Borel Sets of Infinite Rank. \textit{Submitted}

\bibitem{dup3} 
\textsc{Duparc}, J., A Hierarchy of Deterministic Context-Free $\omega$-languages.
Theoretical Computer Science \textsc{290}, 1253--1300, 2003.


%\bibitem{dm7}
%\textsc{Duparc} J., \textsc{Murlak} F. : On the Topological Complexity of Weakly Recognizable Tree Languages. \textit{FCT 2007}, LNCS 4639: 261-273 (2007)

\bibitem{kechris}
\textsc{Kechris} A., \emph{Classical Descriptive Set Theory}, Springer, \textsc{1995}.


\bibitem{martin} 
\textsc{Martin} D.A., \emph{Borel determinacy}, The Annals of Mathematics, \textsc{102} (1975), 363--371.

\bibitem{murlak}
\textsc{Murlak} F., \emph{The Wadge Hierarchy of Deterministic Tree Languages}, ICALP \textsc{2006}, 408--419. 

\bibitem{niwalu}
\textsc{Niwiński} D. and \textsc{Walukiewicz} I., \emph{A gap property of deterministic tree languages}, Theoretical Comput. Sci. \textsc{303} (2003), 215--231.

\bibitem{niwalu2}
\textsc{Niwiński} D. and \textsc{Walukiewicz} I., \emph{Deciding nondeterministic hierarchy of deterministic tree automata},
Electr. Notes Theor. Comput. Sci., \textsc{123} (2005), 195--208.


\bibitem{pinperrin}
\textsc{Perrin} D, \textsc{Pin} J.E., \emph{Infinite Words: Automata, Semigroups, Logic and Games}, Academic Press, \textsc{2004}.

\bibitem{rabin}
\textsc{Rabin} M.O., \emph{Weakly definable relations and special automata}, in Foundations of Set Theory, Y. Bar-Hillel ed., \textsc{1970}, 1--23.

\bibitem{wadge}
\textsc{Wadge} W.W., \emph{Reducibility and Determinateness on the Baire Space}, Ph.D. Thesis, Berkeley, \textsc{1984}.

\bibitem{wagner}
\textsc{Wagner} K., \emph{On $\omega$-regular sets}, Inform.~and Control, \textsc{43}, 123--177, 1979. 

\end{thebibliography}
